О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Add observation about known diameters
Cosmetics

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{lemma}[theorem]{Lemma}

@@

@@

\begin{theorem}
	For every $\varepsilon > 0$ there exists such a number $k_0$, that for every $k>k_0$ we have the inequality
	\begin{equation}
		d(2,k) \geq k\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
		.
	\end{equation}
\end{theorem}

>>>>

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}

@@

Basing on the exact values of $d(2,n)$ for $ 3 \geq n\leq 122$ and the estimate $d(2,123)>10000$
\cite{kurz2008bounds}, we derive
\begin{observation}
	The inequality
	\begin{equation}
		d(2,n) \geq 3^{1/4}\cdot2^{-3/2} \cdot n
	\end{equation}
	holds for $4 \leq n \leq 21491$.
\end{observation}

@@

\begin{theorem}
	For every $\varepsilon > 0$ there exists such a number $n_0$, that the inequality
	\begin{equation}
		d(2,n) \geq n\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
	\end{equation}
	holds for every $n>n_0$.
\end{theorem}
